One-arm spirals in locally isothermal, radially structured self-gravitating discs

### 2014-11-09 paper/paper.tex
udpated

% but also natural in GI. when/where does it happen? 
Spiral arms are also naturally associated with gravitational
instability in differentially rotating discs.

>>>>

% but also natural in GI.
Spiral arms are also naturally associated with global gravitational 
instability (GI) in differentially rotating discs
\citep{laughlin96b,laughlin98,lodato05,forgan11}. Large-scale spiral
arms may provide significant angular momentum transport to enable
accretion \citep{papaloizou91,balbus99,lodato04}, and spiral
structures are potentially observable with the Atacama Large
Millimeter/sub-millimeter Array \citep{cossins10,dipierror14}.

% when/where does it happen? formation stage/dead zones (special for ppd)
GI can be expected in the earliest stages of
circumstellar disc formation \citep{inutsuka10,tsukamoto13}. %also
% outer parts
In the case of protoplanetary discs, which have complex structure
\citep{armitage10}, GI may also occur in `dead
zones'. Indeed, the original motivation for our study was to clarify
exactly what type of GI is relevant to dead zones?
